Predicting political party affiliation from text

### 2016-06-26 manuscript/poltext.tex
fb parser with more functionality - added news download and text cleaning - flattened likes per post

\subsection{Misclassification and policy change}
Automatic political text analysis requires a profound understanding of the models used. One way to better understand these models is to inspect the misclassifications of a model: a potential explanation for the misclassifications could be that parties change their policy positions over time. 
%If a party adapts positions from another party during the legislative period this can lead to misclassification of the previously written respective manifesto text. 
The confusion matrix for the 17th Bundestag in \autoref{tab:confusion_topic} shows that the SPD manifesto texts are often predicted as belonging to the CDU/CSU on the topic level. This was the the legislative period when the CDU under chancellor Merkel was making a strong left move with respect to socioeconomic issues. \\
% there were concrete examples (17th bundestag social reforms -> SPD mixed up with CDU/CSU, 18th bundestag fukushima -> CDU/CSU mixed up with green party), which can not be included due to space constraints. we might leave this out then? 
% Ich habe bei der section immer noch etwas Bauchschmerzen, habe jetzt nochmal umformuliert und versucht doch ein example unterzubringen.

>>>>

\subsection{Misclassification and policy change}
Automatic political text analysis requires a profound understanding of the models used. One way to better understand these models is to inspect the misclassifications of a model. A potential explanation for the misclassifications could be that parties change their policy positions over time. 
%If a party adapts positions from another party during the legislative period this can lead to misclassification of the previously written respective manifesto text. 
The confusion matrix for the 17th Bundestag in \autoref{tab:confusion_topic} shows that the SPD manifesto texts are often predicted as belonging to the CDU/CSU on the topic level. This was the the legislative period when the CDU under chancellor Merkel was making a strong left move with respect to socioeconomic issues. \\
% there were concrete examples (17th bundestag social reforms -> SPD mixed up with CDU/CSU, 18th bundestag fukushima -> CDU/CSU mixed up with green party), which can not be included due to space constraints. we might leave this out then? 
% Ich habe bei der section immer noch etwas Bauchschmerzen, habe jetzt nochmal umformuliert und versucht doch ein example unterzubringen.
